Planar Maximal Covering with Ellipses

### 2019-04-25 quali/quali.presentation/slides.tex
WIP

%\usepackage{hyperref}
\usepackage{tikz}
\usetikzlibrary{quotes, angles, intersections}

%MEUS COMANDOs
\newcommand{\R}{\mathbb{R}}
\newcommand{\D}{\mathscr{D}}
\newcommand{\Pp}{\mathscr{P}}
\newcommand{\Cc}{\mathscr{C}}
\newcommand{\E}{\mathscr{E}}

@@

@@

\section{Introdução}
\begin{frame}
\frametitle{Introdução}
\begin{itemize}
	\item Covering problems
	\begin{itemize}
		\item Set Cover Problem
		\item Maximal Covering Problem
	\end{itemize}
	\item Maximal Covering Location Problem (MCLP)
	\item Planar Maximal Covering Location Problem (PMCLP)
	\begin{itemize}
	\item One disk: $\bigO(n^2)$ and $\bigO(n^2\log{n})$ algorithms
	\item $m$ disks: $\bigO(n^{2m-1}\log{n})$ algorithm
	\end{itemize}
	\item Goals
	\begin{itemize}
		\item Develop a $\bigO(n^2\log{n})$ algorithm for the one disk case
		\item Adapt it for the $m$ ellipses case
	\end{itemize}
\end{itemize}

@@

	\begin{block}{Norms}
		Let $u \in \R^2$ and $Q$ a $2$ by $2$ positive definite matrix
		\begin{itemize}
			\item Euclidean
			\begin{equation*}
			||u||_2 = \sqrt{u^Tu}
			\end{equation*}

@@

@@

	\begin{block}{Ellipse}
		Given a center $c \in \R^2$ and a p.d. matrix $Q$, an ellipse is the set of points that satisfy

		\begin{equation*}
		||u-c||_Q = 1
		\end{equation*}

@@

		\begin{equation*}
		\frac{(x-c_x)^2}{a^2} + \frac{(y-c_y)^2}{b^2} = 1
		\end{equation*}
	\end{block}

@@

		\caption{Three curves representing the points that have distance equal to one.}
		\input{figures/a.tex}
		%\fautor
		\label{fig:3ellipses_intersect}
	\end{figure}
\end{frame}

@@

	\begin{itemize}
		\item $\Pp=\{p_1,\dots,p_n\}$ is the demand set with weights $w(p_i)>0$
		\item $w(A)$, with $A\subset \Pp$ is the sum of weights of the points in $A$
		\item $D(q)$ is a disk with radius one with center at point $q$
		\item We will introduce an equivalent problem...
	\end{itemize}
\end{frame}

@@

	\begin{itemize}
		\item The disks are fixed at $\Pp =\{p_1,\dots,p_n\}$ with $w_k=w(p_k)$
		\item A clique is a non-empty intersection area of a subset of disks
		\item An optimal solution for the maximum weight clique is an optimal solution for $MCD(\Pp,1)$.
	\end{itemize}
\end{frame}

>>>>

%\usepackage{hyperref}

%MEUS COMANDOs

\usepackage{tikz}
\usetikzlibrary{quotes, angles, intersections}
\newcommand{\R}{\mathbb{R}}
\newcommand{\D}{\mathscr{D}}
\newcommand{\Pp}{\mathscr{P}}
\newcommand{\Cc}{\mathscr{C}}
\newcommand{\E}{\mathscr{E}}

@@

\usepackage{pgfplots}
\pgfplotsset{compat=1.4}
%\usepgfplotslibrary{external}
%\tikzexternalize

%FIM MEUS COMANDOS

@@

\section{Introduction}
\begin{frame}
\frametitle{Introduction}
\begin{itemize}
	\item Covering problems
	\begin{itemize}
		\item Set Cover Problem
		\item Maximal Covering Problem
	\end{itemize}
	\item Maximal Covering Location Problem (MCLP)
	\item Planar Maximal Covering Location Problem (PMCLP)
	\begin{itemize}
	\item One disk: $\bigO(n^2)$ and $\bigO(n^2\log{n})$ algorithms
	\item $m$ disks: $\bigO(n^{2m-1}\log{n})$ algorithm
	\end{itemize}
	\item Goals
	\begin{itemize}
		\item Develop a $\bigO(n^2\log{n})$ algorithm for the one disk case
		\item Adapt it for the $m$ ellipses case
	\end{itemize}
\end{itemize}

@@

	\begin{block}{Norms}
		Let $u \in \R^2$ and $Q$ a $2x2$ positive definite matrix
		\begin{itemize}
			\item Euclidean
			\begin{equation*}
			||u||_2 = \sqrt{u^Tu}
			\end{equation*}

@@

		\caption{The elliptical and euclidean norms.}
		\input{figures/elliptical.and.euclidean.norms.tex}
		%\fautor
		\label{fig:3ellipses_intersect}
	\end{figure}
\end{frame}

@@

	\begin{block}{Ellipse}
		Given a center $c \in \R^2$ and a $2x2$ p.d. matrix $Q$, an ellipse is the set of points that satisfy

		\begin{equation*}
		||u-c||_Q = 1,
		\end{equation*}

@@

		\begin{equation*}
		\frac{(x-c_x)^2}{a^2} + \frac{(y-c_y)^2}{b^2} = 1,
		\end{equation*}

		where $(a,b)$ are the shape parameters and $c=(c_x,c_y)$ is the center.
	\end{block}

@@

@@

	\begin{itemize}
		\item $\Pp=\{p_1,\dots,p_n\}$ is the demand set with weights $w(p_i)>0$
		\item $w(A)$, $A\subset \Pp$, is the sum of weights of the points in $A$
		\item $D(q)$ is a unit disk with center at point $q$
		\item We will introduce an equivalent problem...
	\end{itemize}
\end{frame}

@@

	\begin{itemize}
		\item The disks are fixed with centers at $\Pp =\{p_1,\dots,p_n\}$ with $w_k=w(p_k)$
		\item A clique is a non-empty intersection area of a subset of disks. We search for only a point in an optimal clique.
		\item An optimal solution for the maximum weight clique is an optimal solution for $MCD(\Pp,1)$.
	\end{itemize}
\end{frame}

\begin{frame}{Maximum Weight Clique Problem}{Equivalence}
		\begin{figure}[H]
		\centering

		\caption{An instance of $MCD(\Pp,1)$.}
		%\input{figures/elliptical.and.euclidean.norms.tex}
      \center{\includegraphics[width=.7\textwidth]{figures/mcd_instance.png}}
		%\fautor
		\label{fig:mcd_instance}
	\end{figure}
\end{frame}

\begin{frame}{Maximum Weight Clique Problem}{Equivalence}
	\begin{figure}[H]
		\centering

		\caption{An instance of $MCD(\Pp,1)$.}
		%\input{figures/elliptical.and.euclidean.norms.tex}
		\center{\includegraphics[width=.7\textwidth]{figures/mwc_instance.png}}
		%\fautor
		\label{fig:max_wieght_clique}
	\end{figure}
\end{frame}

\begin{frame}{Maximum Weight Clique Problem}{Algorithm}
	Let $\Gamma_+(i,j)$ and $\Gamma_-(i,j)$ be the opening and closing angles of intersections of disks $i$ and $j$. Also, $\Gamma_+(i,j), \Gamma_-(i,j) \in [0,2\pi]$.
	\begin{figure}[H]
		\centering

		\caption{Three disks and their intersection points.}
		\input{figures/img2.tex}
		%\fautor
		\label{fig:3disks_intersect}
	\end{figure}
\end{frame}

\begin{frame}{Maximum Weight Clique Problem}{Algorithm}
	For a disk $D_i$, a counter-clockwise traversal visits every $\Gamma_+(i,j)$ and $\Gamma_-(i,j)$ in counter-clockwise order.

	\begin{itemize}
		\item An intersection region of disks is bounded by arcs.

		\item The arc $\Gamma_+(i,j),\Gamma_-(i,j)$ (counter-clockwise) determines a region where $i$ and $j$ intersect.

		\item In a counter-clockwise traversal, the arcs where $\Gamma_+(i,j) > \Gamma_-(i,j)$ can be a problem for the implementation. Work-around: repeat it.
	\end{itemize}
\end{frame}

\begin{frame}{Maximum Weight Clique Problem}{Algorithm}

	The algorithm is described simply as:

	For every disk, traverse the sorted list of intersection angles twice, keeping a set of active disks, and the current best solution.

\begin{figure}[H]
	\centering

	\caption{The intersections list of a disk with three other disks.}
	\input{figures/fig:array_disks.tex}
%	\fautor
	\label{fig:array_disks}
\end{figure}
\end{frame}

\begin{frame}{Maximum Weight Clique Problem}{Algorithm}

	The run-time complexity of the algorithm is $\bigO(n^2\log{n})$.

	\begin{itemize}
		\item There are $\bigO(n^2)$ intersections among $n$ disks

		\item Sorting takes $\bigO(n^2\log{n})$

		\item The traversal takes $\bigO(n)$ for every disk.

		\item Can be implemented in $K\log{n}$ where $K$ is the number of intersections. 
	\end{itemize}

\begin{block}{Multiple disks}
	For every disk, try every possible assignment that the traversal goes through.
\end{block}
